Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2<-
  cut(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMeanThisSample, c(-10,-1,1,10), 
                                                              labels = c("low", "mid", "high"))

@@

  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
  #              se = F, alpha = .15, size = 1.5)+
  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  # xlim(0,6)+
  facet_grid(~mediansplit_sample_valence2)
# plot separatelly

>>>>

tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2<-
  cut(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMeanThisSample, 3, 
                                                              labels = c("low", "mid", "high"))

tmp.df4_full_stim_downs_jun2021_60bins$sample_valence_lab2<-
  cut(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMeanThisSample, 3 , 
                                                              labels = c("negative", "mid", "positive"))

tmp.df4_full_stim_downs_jun2021_60bins$newvalence <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$sample_valence_lab2 == "mid" & tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2 == "mid", "neutral", 
                                                             if_else(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMeanThisSample> median(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMeanThisSample, na.rm = TRUE), "positive", "negative")
                                                           )

table(tmp.df4_full_stim_downs_jun2021_60bins$newvalence)
unique(tmp.df4_full_stim_downs_jun2021_60bins$newvalence)

@@

  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
               # se = F, alpha = .15, size = 1.5)+
  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")

  # stat_smooth(aes(group= stimIAPS, color = sample_valence_lab2), fun = mean,
  #              se = F, alpha = .15, size = 1.5)+
  stat_smooth(aes(group=newvalence, color = newvalence), size = 3)+
  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")
  facet_grid(~newvalence)

```
  # xlim(0,6)+
  facet_grid(~mediansplit_sample_valence2)
# plot separatelly

  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
  #              se = F, alpha = .15, size = 1.5)+
  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")
  # xlim(0,6)+
  facet_grid(~mediansplit_sample_valence2)

  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
  #              se = F, alpha = .15, size = 1.5)+
  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # geom_text(aes(label = stimIAPS))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")
